---
title: "bc_ltc_analysis"
author: "Ngan Lyle"
date: "21/08/2020"
output: html_document
---

## Import and prepare the data
```{r results="hide"}
library(skimr)
library(dplyr)



# Import the data

# noNHorVIHA data
df <- read.csv("../data/BC/bc_ltc_noNHorVIHA.csv", na.strings="", header=TRUE)
str(df)

# selected data (remove all predictors with missing values)
# df <- read.csv("../data/BC/bc_ltc_selected.csv", na.strings="", header=TRUE)
# 
# # Remove the 3 homes that are considered "Special Units"
# df <- df %>% 
#   filter(!grepl('Special Unit', FACILITY_NAME))
# 
# str(df)
```

```{r, echo=FALSE}
# Change datatypes as needed
listofcol = list('FACILITY_NAME', 'HCC_CODE', 'STREET_ADDRESS', 'CITY', 'POSTAL')
for (each in listofcol){
  df[, each] <- as.character(df[, each])
}

df$outbreak <- as.factor(df$outbreak)
# str(df)
dput(names(df))
```

```{r, include=FALSE}
# # Generate the data for analysis
# # Create lists of variables used to filter data for analysis

# # selected data
# num <- c("BEDS_TOTAL", "BEDS_PRIVATEprop", "ROOMS_PRIVATE", "ROOMS_SEMI", "ROOMS_MULTI")
# cat <- c("HLTH_AUTH", "OWNERSHIP", "REGULATION", "ACCRED_STATUS", "RESIDENT_COUNCIL", "FAMILY_COUNCIL")
# data <- subset(df, select = c(num, cat, 'outbreak'))

# noNHorVIHA data
incidents = c(
  "INCIDENT_OUTBREAK_100",
  "INCIDENT_ABUSE_100", "INCIDENT_FALL_100", "INCIDENT_POISON_100",
  "INCIDENT_MEDICATION_100", "INCIDENT_WANDERING_100",
  "INCIDENT_INJURY_100", "INCIDENT_AGGRESSION_100"
  )

inspections = c(
  "COMPLAINTS", "SUB_COMPLAINTS", "INSPECTIONS",
  "INFRACTIONS",
  "INFRACTIONS_DISEASE")

gen = c("OWNERSHIP", "REGULATION", "ACCRED_STATUS","RESIDENT_COUNCIL", "FAMILY_COUNCIL")

dch = c(
  "DCH_NURSE_LASTYR", 
  "DCH_ALLIED_LASTYR", 
  "DCH_NURSE_CURRENTYR",
  "DCH_ALLIED_CURRENTYR"
 )

space = c("BEDS_PRIVATEprop", "BEDS_TOTAL",
  "ROOMS_PRIVATE", "ROOMS_SEMI", "ROOMS_MULTI")

dem = c(
  "AGE", "FEMALE", 
  "AGE_85_PLUS", "AGE_UNDER_65", "DEPRESSION", "ADL_DEPENDENT", 
  "CPS_SEVERE", "DEMENTIA", "ABS_PHYS_ABUSIVE", "ISE_LOW", "CMI", 
  "THERAPY_PT", "THERAPY_RT", "THERAPY_OT", "MEDS_DEPRESSION", 
  "MEDS_ANTIPSYCHOTICS", "RESTRAINTS"
)

data <- subset(df, select = c(gen, incidents, inspections, dch, space, 'outbreak'))

str(data)
```



```{r, }
## Assessing skewness
# Check for R skewness in numeric predictors
library(e1071)

listofcols = c(num)

for (each in listofcols){
  print(each)
  print(skewness(data[[each]]))
  qqnorm(data[[each]], main = each)
  qqline(data[[each]], col = 'red')
}

# listofcols = c(incidents, inspections, "CMI", dch, space)
# 
# for (each in listofcols){
#   print(each)
#   print(skewness(data[[each]]))
#   qqnorm(data[[each]], main = each)
#   qqline(data[[each]], col = 'red')
# }

```


All the data are right skewed except for 
  1. BEDS_PUBLICprop 3.430426
  2. ROOMS_PRIVATEprop -1.486055

```{r, include=FALSE}
# Assess variables for 0s
for (each in listofcols){
  print(each)
  print(summary(df[[each]]))
}

```

Most numeric variables have 0s except for:
- CMI
- all DCH variables
- BEDS_PUBLIC, 1.142218
- BEDS_TOTAL, 1.03226
- ROOMS_PRIVATE, 0.944784
- BEDS_PUBLICprop, 3.430426 highly L skewed
- ROOMS_TOTAL, 1.103714
- ROOMS_PRIVATEprop, -1.486055 slightly R skewed

## Explore the variables for transformation
```{r, fig.show="hide"}

# Create a list of right skewed numeric variables with 0 values
list_non0s = c('BEDS_TOTAL')
list0s = c("ROOMS_PRIVATE", "ROOMS_SEMI", "ROOMS_MULTI",
  "BEDS_PRIVATEprop")


# # Create a list of right skewed numeric variables with 0 values
# space_non0s = c('BEDS_PUBLIC', 'BEDS_TOTAL', 'ROOMS_PRIVATE', 'ROOMS_TOTAL')
# space_0s = c("BEDS_PRIVATE", "ROOMS_SEMI", "ROOMS_MULTI",
#   "BEDS_PRIVATEprop", "ROOMS_SEMIprop", "ROOMS_MULTIprop")
# 
# list0s <- c(incidents, inspections, space_0s)
# list_non0s <- c(space_non0s, dch, 'CMI')
# left_skewed <- c('BEDS_PUBLICprop', 'ROOMS_PRIVATEprop')

library(rcompanion)
# listofcols <- setdiff(listofcols, list0s)

# Visualize the effect of square root transformations on the numeric predictors
for (each in num) {  
  plotNormalHistogram(x = data[[each]], main = each)
  plotNormalHistogram(x = sqrt(data[[each]]), main = c(each, 'sqrt trans'))
}

# Visualize the effect of log transformations on the data with no 0s that are right skewed
for (each in list_non0s) {  
  plotNormalHistogram(x = data[[each]], main = each)
  plotNormalHistogram(x = log(data[[each]]), main = c(each, 'log trans'))
}

# Visualize the effect of transformations on the data that are left skewed
# # log10(max(x+1) - x)
# plotNormalHistogram(x = data[['BEDS_PUBLICprop']])
# plotNormalHistogram(x = sqrt(max(data[['BEDS_PUBLICprop']] + 1) - data[['BEDS_PUBLICprop']]))

# # sqrt(max(x+1) - x)
# plotNormalHistogram(x = data[['ROOMS_PRIVATEprop']])
# plotNormalHistogram(x = sqrt(max(data[['ROOMS_PRIVATEprop']] + 1) - data[['ROOMS_PRIVATEprop']]))

```
Sqrt transformation is best for all the data.


## Transform the data
```{r }
# list0s
# # Sqrt transform in place
# data[list0s] <- log(data[list0s])

# Square root transform in place
data[num] <- sqrt(data[num])

skim(data)
```

## Fit logistic regression
```{r }
# Fit logistic regression using transformed data
fit = glm(outbreak~., family=binomial, data=data)
summary(fit)
```

### Backwards selection
```{r, include=FALSE}
fit <- update(fit, .~. -HLTH_AUTH)
summary(fit)
fit <- update(fit, .~. -REGULATION)
summary(fit)
fit <- update(fit, .~. -BEDS_PRIVATEprop)
summary(fit)
fit <- update(fit, .~. -ROOMS_PRIVATE  )
summary(fit)
fit <- update(fit, .~. -ROOMS_MULTI)
summary(fit)
fit <- update(fit, .~. -RESIDENT_COUNCIL)
summary(fit)
fit <- update(fit, .~. -ROOMS_SEMI)
summary(fit)

fit <- update(fit, .~. -ACCRED_STATUS)
summary(fit)
fit <- update(fit, .~. -OWNERSHIP)
summary(fit)

```

```{r }
hist(data$BEDS_TOTAL)

# Most homes have a family_council
# 8/46 homes without a family council had an outbreak
# 26/251 with a family council had an outbreak
xtabs(~outbreak + FAMILY_COUNCIL, data=df)

# Review the minority of homes without a family council
subset(df, FAMILY_COUNCIL == 'False')
```

```{r }

```

```{r }

```

