---
title: "phu_analysis"
author: "NL"
date: "27/05/2020"
output: html_document
---


```{r, echo=FALSE}
# Import the necessary libraries
library(skimr)
```

## Import data
```{r }
# Import the PHU data
df_source = read.csv(file = 'merged_data_BC_HSD.csv', stringsAsFactors = FALSE, na.strings="", header=TRUE)
colnames(df_source)
str(df_source)
# skim(df)
# rownames(df)
# head(df)
# df[is.na(df$Chronic.obstructive.pulmonary.disease..COPD..35.years.and.over.),]
```

## Clean data
Four variables with missing values: 

1. prox_idx_transit_med (Median proximity measure to transit) and Chronic.obstructive.pulmonary.disease..COPD..35.years.and.over. - **impute 0**

2. Breast.milk.feeding.initiation - **remove**

3. Exclusive.breastfeeding..at.least.6.months - **remove**

4. Body.mass.index..self.reported..youth..12.to.17.years.old...overweight.or.obese - **remove**

We remove the columns that are not needed and we will use weighted proximity scores rather than the median proximity scores. This leaves us with 55 predictor variables and 2 response variables. 

The predictor variables include:

1. Census variables (e.g. age, housing, income, education, employment) - 26

2. Proximity variables (e.g. transit, parks, grocery) - 10

3. Health variables (e.g. asthma, perceived health, obesity) - 19

The response variables are proportion (as a fraction of the population in the health region) of cases and fatalities. 

```{r, echo=FALSE}
df <- df_source

# Create a column with colors corresponding to urban classification
df$peer_col <- ifelse(df$peer_char == "Large urban", 'red',
                  ifelse(df$peer_char == "Moderate urban", 'gold',
                         ifelse(df$peer_char == "Urban-rural mix", 'dodgerblue', 'dodgerblue4')))


# COPD - impute 0
# Consider imputing with a different value, neighboring HSD or based on proportion smokers
df$Chronic.obstructive.pulmonary.disease..COPD..35.years.and.over.[is.na(df$Chronic.obstructive.pulmonary.disease..COPD..35.years.and.over.)] <- 0

# colnames(df)

# Breastfeeding variables and obesity in youth - remove
# Remove other variables not needed
df <- df[,-c(1:2, 4:7, 34, 45:54, 59:61, 65, 80:81)] 
# df <- df[,-c(1:2, 4:32, 43:79)] # Include just the proximity measures as predictors
# df <- df[,-c(1:2, 4:5, 32, 43:52, 56:58, 60, 63, 76, 78:79)] # Remove median prox scores

# rownames(df) <- df[,1]

# Convert percent data to proportions: 1. age group data 2. health data
# df[, c(16:34)] <- df[, c(16:34)]/100

colnames(df)
# skim(df)
# head(df)

```

## PCA on the data
```{r }
pca <- prcomp(df[,-c(1, 59:60)], scale = TRUE)
s <- summary(pca)

```

```{r }
# Scree plot
plot(pca, type="lines")

```

# Graph the PCA
```{r }
# PCA graph using the base graphics function plot()
# plot(pca$x[,1], pca$x[,2])

# Create groups
pch.group <- rep(21, times=16)

# PCA graph using the base graphics function plot()
plot(pca$x[,1], pca$x[,2], xlab=paste("PC1 (", round(s$importance[2]*100, 1), "%)", sep = ""), ylab=paste("PC2 (", round(s$importance[5]*100, 1), "%)", sep = ""), pch=pch.group, col="black", bg=df$peer_col, cex=1.5, las=1, asp=1)

# Add grid lines
abline(v=0, lty=2, col="grey50")
abline(h=0, lty=2, col="grey50")

# Add legend
legend("bottomright", legend=c("Large urban", "Moderate urban", "Urban-rural mix", "Rural"), col="black", pt.bg=c("red", "gold", "dodgerblue", "dodgerblue4"), pch=c(21, 21, 21, 21), pt.cex=1.5)

```

```{r }
# Biplot
biplot(pca, col = c("blue", "red"), cex = c(0.5,0.5))
# pca
```

## Principal components regression (PCR) against proportion of cases
```{r }
# pca$x <- -pca$x
# pca$rotation <- -pca$rotation

# Extract the PCs for PCR
# pcs <- pca$x[,c("PC1", "PC2", "PC3", "PC4", "PC5", "PC6")]
pcs <- pca$x[,c("PC1", "PC2")]

# Create a dataframe with response variable TOTAL proportion of COVID cases and explanatory variables (the PCs)
pcr_data <- as.data.frame(cbind(df_source[,"HSDPOP"], df[,"count_prop"], pcs))
head(pcr_data)

# Perform regression
phu_lm_total <- lm(V2 ~ . -V1, data = pcr_data, weights = V1)
summary(phu_lm_total)

```

## Review PC 1
```{r, echo=FALSE }
pca$rotation[,c(1)]

```

## Review the top loading scores
```{r }
loading_scores <- pca$rotation[,1]
var_scores <- abs(loading_scores)

# Rank and show the top 10 loading score by magnitude
var_scores_ranked <- sort(var_scores, decreasing = TRUE)
top_10_var <- names(var_scores_ranked[1:10])
top_10_var

pca$rotation[top_10_var, 1] 
```



```{r, include=FALSE }
# library(ggplot2)
# library(grid)
# library(RColorBrewer)
# # colnames(df_source)
# density <- df_source[, 6]
# PCbiplot <- function(PC, x="PC1", y="PC2") {
#     # PC being a prcomp object
#     data <- data.frame(obsnames=row.names(PC$x), PC$x)
#     plot <- ggplot(data, aes_string(x=x, y=y)) + geom_point(aes(colour = density), alpha=1, size=2) + scale_color_gradient(low = "blue", high = "orange red")
#     plot <- last_plot() + theme_minimal()
#     # plot <- ggplot(data, aes_string(x=x, y=y)) + geom_text(alpha=.6, size=2.5, aes(label=obsnames))
#     # plot <- plot + geom_hline(aes(0), size=.2) + geom_vline(aes(0), size=.2)
#     datapc <- data.frame(varnames=rownames(PC$rotation), PC$rotation)
#     mult <- min(
#         (max(data[,y]) - min(data[,y])/(max(datapc[,y])-min(datapc[,y]))),
#         (max(data[,x]) - min(data[,x])/(max(datapc[,x])-min(datapc[,x])))
#         )
#     datapc <- transform(datapc,
#             v1 = .7 * mult * (get(x)),
#             v2 = .7 * mult * (get(y))
#             )
#     plot <- plot + coord_equal() + geom_text(data=datapc, aes(x=v1, y=v2, label=varnames), size = 3.5, vjust=1, color="red")
#     plot <- plot + geom_segment(data=datapc, aes(x=0, y=0, xend=v1, yend=v2), arrow=arrow(length=unit(0.2,"cm")), alpha=0.75, color="red")
#     plot
# }
# 
# PCbiplot(pca)

```


```{r, include=FALSE }
# # Use ggplot2 to plot the data
# library(ggplot2)
# pca.data <- data.frame(Sample = df$ENG_LABEL, X=pca$x[,1], Y=pca$x[,2])
# pca.data
# 
# ggplot(data=pca.data, aes(x=X, y=Y, label = Sample)) +
#   geom_text() + geom_point() +
#   xlab(paste("PC1 - ", pca.var.per[1], "%", sep = "")) +
#   ylab(paste("PC2 - ", pca.var.per[2], "%", sep = "")) +
#   theme_bw() +
#   ggtitle("PCA Graph")

```


```{r, include=FALSE }
## Factor Analysis
# Extract the predictor columns
# df2_prop2 <- df2_prop[,-c(1,2,3)]
# df_med2 <- df_med[,-c(1:4, 37:48)]


# Check KMO, Bartletts which tells us if FA is appropriate
# KMO values between 0.8 and 1 indicate the sampling is adequate.
# KMO values less than 0.6 indicate the sampling is not adequate and that remedial action should be taken. Some authors put this value at 0.5, so use your own judgment for values between 0.5 and 0.6.
# KMO Values close to zero means that there are large partial correlations compared to the sum of correlations. In other words, there are widespread correlations which are a large problem for factor analysis.
library(psych)

# KMO(cor(df2_prop2))
colnames(df)
KMO(cor(df[,-c(1, 59:60)]))
# We look for MSA > 0.5
# The following variables have MSA < 0.5
# Asthma
# Body.mass.index..adjusted.self.reported..adult..18.years.and.over...overweight
# Diabetes
# Has.a.regular.healthcare.provider
# Influenza.immunization.in.the.past.12.months
# Life.satisfaction..satisfied.or.very.satisfied
# Perceived.life.stress..most.days.quite.a.bit.or.extremely.stressful
# Perceived.mental.health..fair.or.poor 
# Perceived.mental.health..very.good.or.excellent 
# Physical.activity..150.minutes.per.week..adult..18.years.and.over. 
# Physical.activity..average.60.minutes.per.day..youth..12.to.17.years.old. 
# Sense.of.belonging.to.local.community..somewhat.strong.or.very.strong
# prox_idx_grocery_med 
# prox_idx_educsec_med 
# prox_idx_lib_med 

# print(cortest.bartlett(cor(df_med2), nrow(df_med2)))
print(cortest.bartlett(cor(df[,-c(1, 59:60)]), nrow(df[,-c(1, 59:60)])))
# Bartletts test of sphericity is significant

```

```{r, eval=FALSE, include=FALSE }
phu_fa <- factanal(df[,-c(1, 59:60)], factors = 6, rotation = "varimax", scores = "regression")
# phu_fa <- factanal(df2_prop2, factors = 2, rotation = "varimax", scores = "regression")
# phu_fa <- factanal(df2_prop2, factors = 2, rotation = 'none')
# phu_fa <- factanal(df2_prop2, factors = 2, rotation = 'promax', scores = c("regression"))
phu_fa

```

```{r, eval=FALSE, include=FALSE}
# Use factor scores as explanatory variables in a regression analysis
phu_fa$scores

total_fa <- as.data.frame(cbind(df[,"TOTALprop"], phu_fa$scores))
# total_fa <- as.data.frame(cbind(df2_prop[,"TOTALprop"], phu_fa$scores))
head(total_fa)

mod = lm (V1~., total_fa)
summary(mod)

```

```{r, include=FALSE }
# # 3d plot
# options(rgl.useNULL = TRUE)
# library(rgl)
# with(total_fa, plot3d(V1, Factor1, Factor2, type="p"))
# triangles3d(total_fa[,1], total_fa[,2], total_fa[,3])
# rglwidget()
# 
# fit <- lm(V1~., total_fa)
# surfacefn <- function(x, y) cbind(1, x, y, z) %*% coef(fit)
# persp3d(surfacefn, add = TRUE, col = "blue")
```


```{r, eval=FALSE, include=FALSE }
# fatal_fa <- as.data.frame(cbind(df2_prop[,"FATALprop"], phu_fa$scores))
fatal_fa <- as.data.frame(cbind(df_med[,"FATAL_prop"], phu_fa$scores))
head(fatal_fa)

mod = lm (V1~., fatal_fa)
summary(mod)

```


```{r, eval=FALSE, include=FALSE }
set.seed(100)
indices= sample(1:nrow(total_fa), 0.7*nrow(total_fa))
train = total_fa[indices,]
test = total_fa[-indices,]

mod = lm (V1~., train)
summary(mod)

library(car)
vif(mod)

# Model Performance metrics:
library(Metrics)

# Model 1:
pred_test1 <- predict(mod, newdata = test, type = "response")
pred_test1

```




```{r }

```


```{r }

```


```{r }

```


```{r }

```


```{r }

```


