---
title: "ltc_analysis_ON_deaths"
output: html_document
---

## Import and prepare the data
```{r }
# library(skimr)
library(devtools)
library(broom)

# Import the data
df <- read.csv("../data_output/merged_LTC_odhf_quality.csv", na.strings="", header=TRUE)
# skim(df)
# head(df)

# Change variable data types
df[, 'outbreak'] <- as.factor(df[, 'outbreak'])

listofcol = list('first_inspection_date', 'date_first_outbreak', 'date_max_cases', 'date_max_HCWcases', 'date_first_resolved')
for (each in listofcol){
  df[, each] <- as.Date(df[, each])
}

listofcol = list('name', 'cleaned_name', 'address', 'city', 'postal_code', 'CSDname')
for (each in listofcol){
  df[, each] <- as.character(df[, each])
}

# skim(df)
str(df)

```


## Determine number years since the first inspection for each home
```{r, results='hide'}
# Create a new column for first inspection year
df$first_inspection_year <- format(df$first_inspection_date,"%Y")
df$first_inspection_year <- as.numeric(df$first_inspection_year)

# Earliest date of first inspection was in 2009 and latest date was 2016
summary(df[['first_inspection_year']])

# Create a new column with number of years since the first inspection was reported
df$years_since_first <- 2020 - df$first_inspection_year
# summary(df[['years_since_first']])

# There is only 1 home with fewer than 5 years of inspections -> Royal Rose Place
table(df['years_since_first'])
subset(df, years_since_first == 4)
```
### Normalize the number of inspections
```{r, results='hide'}
# Number of inspections/beds
df$total_inspections_norm <- df$total_inspections/df$number_beds/df$years_since_first
df$X5y_inspections_norm <- df$X5y_inspections/df$number_beds/5
df[293, "X5y_inspections_norm"] <- df[293, "X5y_inspections_norm"]*5/4
df$X2y_inspections_norm <- df$X2y_inspections/df$number_beds/2

# Number of withOrders/beds
df$total_withOrders_norm <- df$total_withOrders/df$number_beds/df$years_since_first
df$X5y_withOrders_norm <- df$X5y_withOrders/df$number_beds/5
df[293, "X5y_withOrders_norm"] <- df[293, "X5y_withOrders_norm"]*5/4
df$X2y_withOrders_norm <- df$X2y_withOrders/df$number_beds/2

# Drop un-normalized inspections data
df <- df[,-c(21:32)]

# dput(names(df))
# skim(df)
str(df)
```
## Subset the data
```{r, }
# Group the data for analysis
# Create lists of variables used to filter data for analysis

outcomes = c(
  "outbreak", 
  "cum_resident_deaths", 
  "max_resident_cases", 
  "max_hcw_cases"
  )

profile = c(
  "home_type", 
  "number_beds", 
  "short_stay", 
  "residents_council", 
  "family_council", 
  "accreditation"
  )

location = c(
  'address', 
  'LHIN', 
  'city', 
  'postal_code', 
  'CSDname', 
  'CSDuid', 
  'latitude', 
  'longitude')

inspections_total = c(
  'total_inspections_norm',
  'total_withOrders_norm'
)

inspections_5y = c(
    'X5y_inspections_norm'
  , "X5y_withOrders_norm"
  )

inspections_2y = c(
    'X2y_inspections_norm'
  , "X2y_withOrders_norm"
  )

inspections = c(inspections_2y, inspections_5y, inspections_total)

```


```{r, }
# As cases/deaths can only occur in homes with an outbreak will subset to include only homes with an outbreak
outbreak <- subset(df, outbreak == 1)

# Look at the distribution of count data
hist(outbreak$cum_resident_deaths)
hist(outbreak$max_resident_cases)
hist(outbreak$max_hcw_cases)

```


```{r }
# Subset data, cumulative resident deaths as outcome
data <- subset(outbreak, select = c('cum_resident_deaths', profile, inspections))
# dput(names(data))

```

LASSO - CovTest
```{r }
x <- model.matrix(cum_resident_deaths~., data = data)[,-1]
y <- data.matrix(data[,1])
a=lars(x,y)
covTest(a,x,y)

a$beta
plot(a)
summary(a)

```

# Modeling the number of deaths
## LASSO for variable selection

```{r, results="hide"}
library(glmnet)
options(max.print= 9999, width = 9999)
# model.matrix() automatically transforms any qualitative variables into dummy variables
# Trim the first column leaving only predictors
x <- model.matrix(cum_resident_deaths/number_beds~., data = data)[,-1]
y <- data.matrix(data[,1])

# Note alpha=1 for lasso only and can blend with ridge penalty down to
# alpha=0 ridge only
glmmod <- glmnet(x, y, alpha = 1)
coef(glmmod)
```

As lambda decreases, the order that predictors are added to the model:
    
    1. home_typeMunicipal
    2. short_stayYes
    3. accreditationYes
    4. residents_councilYes
    5. family_councilYes


```{r }
# Plot variable coefficients vs. shrinkage parameter lambda
plot(glmmod, xvar = 'lambda', label = TRUE)
plot(glmmod, xvar = 'dev', label = TRUE)

# LASSO - CV
grid = exp(seq(-5, 5, length=100))
cv.glmmod <- cv.glmnet(x, y, alpha=1, lambda = grid)
# cv.glmmod <- cv.glmnet(x, y, alpha=1)
plot(cv.glmmod)
coef(cv.glmmod)
coef(cv.glmmod, s = "lambda.min")
```

    
# Poisson regression with offset for the number of beds in each home
```{r }
# fit_poi <- glm(Total.Confirmed.Cases/BEDS_TOTAL~ ., family = poisson, data = data_cases, weight = BEDS_TOTAL)
# summary(fit_poi)

fit_poi <- glm(cum_resident_deaths~ 
    home_type
    + short_stay
    + residents_council
    + family_council
    + accreditation
    # + X2y_inspections_norm
    # + X2y_withOrders_norm
    # + X5y_inspections_norm
    # + X5y_withOrders_norm
    # + total_inspections_norm
    # + total_withOrders_norm
    , family = poisson, data = data, offset = log(number_beds))
summary(fit_poi)

```



```{r }

```


```{r }

```


```{r }

```


```{r }

```

